\documentclass{soft-cover}

\themeColor{cvDarkBlue}
\name{Christopher Poenaru}
\email{kiambogo@gmail.com}
\web{chrispoenaru.com}
\linkedin{chrispoenaru}
\github{kiambogo}

\companyName{HashiCorp}
\companyAddress{101 2nd St #700\\San Francisco, CA\\94105\\United States}

\position{Senior Software Engineer, Consul Core}

\body{
  Dear Sir/Madam,

  \vspace{0.5cm}

  % Introduce yourself
  I am writing this letter as part of my application for the position of \textbf{Senior Software Engineer, Consul Core}.
  I am a software engineer with 5+ years of experience architecting, designing, and building scalable web and backend services.
  This experience has instilled in me the importance of delivering high-quality, tested, and easy-to-read code.
  With over 5 years of working remote for several different companies and teams, I am well-versed with being self-motivated, productive, and collaborative on a decentralized team.

  \vspace{0.5cm}

  % Explain why you're interested in the company
  With an exceptionally strong company foundation of innovation and engineering excellence (engrained in the \textit{Tao of HashiCorp}) in addition to an emphasis on decentralized teams and open source software, HashiCorp has always stood out to me amongst the other tech giants.
  The concept of `Workflows, not technologies' particularily resonsates with me, as I have seen firsthand how technologies can come and go in a short period of time, yet many of the fundamental problems remain the same.
  HashiCorp preserves focus on the big picture instead of getting lost in the details, which inspires confidence in me that the products it releases will continue to be useful in the future.
  Finally, as someone who has learned a great deal from browsing and reading open source code repositories, I always seek to give back to the open source community wherever possible.
  It is nothing short of exemplary that HashiCorp releases their core products as open source to the community, which in turn fosters a better development experience for all.

  \vspace{0.5cm}

  % Explain why you're interested in the role
  I first was acquainted with Consul when I was researching into service discovery patterns many years ago.
  I was impressed with Consul as a product that aims to reduce the complexity and barrier to entry for multi-service deployments and operations, but even more impressed that software of this caliber was released as open source.
  I believe that we are now in an age where almost all of developer operations and infrastructure can be automated - saving companies time, money, and allowing them to focus their efforts on releasing their product instead of the scaffolding to get there.
  I see Consul as one of the most advanced service mesh offerings on the market, and would be thrilled to contribute to make it even better.

  \vspace{0.5cm}

  % Conclusion
  I believe that I would make a strong addition to the already world-class team of engineers at HashiCorp, and would contribute to reducing the friction companies face when setting up infrastructure.
  Thank you for your time and consideration.

}

% Ensure that document defintion is at the bottom
\begin{document}
    {\mkHeader}
    {\mkBody}
\end{document}
